\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-04 doc/sw-system.tex
\todo items for Phil and Chris
Fixed #43 in discussion section (#44) by adding illustrative images and trajectories. Closed #68 as well, in the process

@@

We first investigate the source of the incompleteness visible in 
\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives.
\Fref{fig:discuss:performance:FNgallery} shows N example simulated lenses that
were missed by the \sw system. In some cases their rejection is
understandable: the lensed features are faint, or otherwise difficult to see.
However, in other cases a reasonably obvious lens was passed over. 
\Fref{fig:discuss:performance:FNtrajectories} shows the probability 
trajectories of these subjects. \todo{Phil}{Make the FN plots, and look for
behaviour. Can we see whether the FNs are due to costly mistakes by expert
classifiers? Or are they just random walking south?}

Is the system's impurity a result of the same behaviour?
Figures~\ref{fig:discuss:performance:FPgallery}
and~\ref{fig:discuss:performance:FPtrajectories} show the corresponding
figures for the false positives -- non-lenses that were incorrectly inferred
to be lens candidates during stage 2. \todo{Phil}{Make the FP plots, and look
for behaviour. Can we see whether the FPs are due to costly mistakes by expert
classifiers? Or are they just random walking south?}

In general, there are three places we can act to improve system performance:
educating the volunteers, assigning subjects for classification, and
interpreting the classification data. The plots in this section suggest that
...
\todo{Phil}{complete this thought, and update the text below, in the light of
the FP and the FN figures}

Mistakes by reasonably high skill classifiers cause large jumps in subject
probability in the wrong direction, as are occasionally visible in the
trajectory plots in this section. We might wonder whether some of those
mistakes could have been corrected by the classifiers themselves, had they had
access to a ``go back'' option. While clearly enabling error reduction, we
might worry about such a mechanism enabling classifiers to have a guess, then
go and read the Talk discussion, and then return to the classification
interface to change their mind to agree with the forum. In fact, this is
already possible on the current interface -- and indeed, it is not obvious
that such correlations would necessarily lead to poorer system performance.
This could be tested by presenting a fraction of the volunteers with a version
of the site that actively suggested that they take this approach, and then
tracking the relative performance of ``collaborative'' classifications
compared with independent ones. We leave this to further work.

@@

Some trajectories show signs of a random walk problem. Those subjects are
simply ``unlucky:'' they are only seen by low skill classifiers, and  happen
to be mis-classified  enough times to cross the retirement threshold (in the
case of the false negatives) or remain in the system (in the case of the false
positives). While improved training will help reduce this effect, it is here
that targeted task assignment could help improve system performance. We
advertised stage 2 of the current project to all registered users; it was
taken up by stage 1 veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since stage 2 was quite short): of
the 1964 volunteers who took part in the stage 2 classification round, only
774 were veterans from stage 1. \Fref{fig:discuss:performance:stage1vstage2}
shows how the stage 1 skill maps on to stage 2 skill and contribution...

\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
size given by stage 2 contribution. Stage 2 newbies will all have 0 +/- small
stage 1 skill. Then move this figure to here.}

Thsi figure suggests that there may be some benefit to opening stage 2 on the
basis of agent skill, in order to reduce the noise in the system generated by
new and low skill volunteers in this more difficult classification stage. A
simple implementation of this would be to switch the web app to the stage 2
version when either a certain stage 1 skill (and/or effort) threshold was
passed. Good strategy would probably be to switch back to stage 1 after some
number of stage 2 classifications (to avoid losing the high skill users from
stage 1 entirely), and also to make it very clear which stage the classifier
was at (since stage 2 requires more careful attention). This is something we
plan to experiment with in future.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}

\vspace{\baselineskip}

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of 
false negatives (blue) and false positives (red) from the classification of
the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right).}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We investigated the source of the incompleteness and impurity visible in 
\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
false positives. \Fref{fig:discuss:performance:trajectories} shows 2 example
simulated lenses  that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw
system, and 2 example non-lenses that were incoreectly flagged as candidates
($\pr(\LENS|C,T) > 0.95$) by the \sw system.

In some cases the rejection of the false negatives is understandable: the
lensed features are faint, or otherwise difficult to see. However, in other
cases a reasonably obvious lens was passed over.  This mainly seems to be due
to noise in the system: when only low-skill classifiers view a subject, all
the updates to its posterior probability are small, and if none are very
confident about the presence of lensing, the subject follows a random walk
down its trajectory plot. This can be seen in the top left panel of the
figure.  The false positives show similar behaviour, for example in the bottom
lefthand panel of the figure. As well as subjects being ``unlucky'' in this
way, there are two less common failure modes associated with mistakes made by
higher skill users, illustrated in the righthand column of the figure. In the
false negative subject shown in the top right-hand panel, several high skill
classifiers update the subject upwards in log probability by some way each
time, but other, comparable skill classifiers mis-classify the system to lower
probability. If we had retired subjects after crossing a high probability
detection threshold, this subject would have been correctly identified as a
lens candidate; instead, it was kept in the system and eventually scattered
down to retirement. The trajectory looks like a random walk, but with bigger
steps. The bottom righthand panel shows an example of a final, apparently
rare, failure mode: we see some short-step random walk behaviour, followed by
a mis-classification by a very high skill ``expert'' classifier after 20
classifications that promotes the subject to high probability.

There are a number of places where we can address these problems and
improve system performance: adding flexibility to the classification
interface, educating the volunteers, assigning subjects for
classification, and interpreting the classification data.

We might wonder whether some of  the mistakes made by reasonably high skill
classifiers could have been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error
reduction, we might worry about such a mechanism enabling classifiers to have
a guess, then go and read the Talk discussion, and then return to the
classification interface to change their mind to agree with the forum. In
fact, this is already possible on the current interface -- and indeed, it is
not obvious that such correlations would necessarily lead to poorer system
performance. This could be tested by presenting a fraction of the volunteers
with a version of the site that actively suggested that they take this
approach, and then tracking the relative performance of ``collaborative''
classifications compared with independent ones. We leave this to further
work.

@@

However, most identification failures (around 60\%) seem to be due to the
random walk problem. While improved training will help reduce this effect, it
is here that targeted task assignment could help improve system performance.
We advertised stage 2 of the current project to all registered users; it was
taken up by stage 1 veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since stage 2 was quite short): of the 1964 volunteers who took part in
the stage 2 classification round, only 774 were veterans from stage 1.
\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
on to stage 2 skill and contribution...

\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
size given by stage 2 contribution. Stage 2 newbies will need to be plotted to
have (0 +/- small) stage 1 skill, to show up as a cloud.}

This figure suggests that there may be some benefit to opening stage 2 on the
basis of agent skill, in order to reduce the noise in the system generated by
new and low skill volunteers in this more difficult classification stage. A
simple implementation of this would be to switch the web app to the stage 2
version when either a certain stage 1 skill (and/or effort) threshold was
passed. Good strategy would probably be to switch back to stage 1 after some
number of stage 2 classifications (to avoid losing the high skill users from
stage 1 entirely), and also to make it very clear which stage the classifier
was at (since stage 2 requires more careful attention). This is something we
plan to experiment with in future.
